\mytitle

### 2016-10-11 pdocs/thesis/article-section-3.tex
added octave plot to section 3

Actual values for unconstrained case without continuous collision detection
are shown in Table \ref{tab:freeBlockValues}. Penetration is detected at time 0.567 s when
{\it velError} is 5.67 (5.5+0.167) and
{\it posError} is 2.8 (0.058*0.8/0.0167). Impulse is 34000 and contact force is thus about 2 MN (34000/0.0167).
After few steps location and position stabilize although internally calculation is needed for each time step
until body is deactivated.

\begin {table}[htb!]
\caption {Simulation values for unconstrained case. 
For internal contact values typical values are shown
as number of contacts and values at contact points are different.} 
\label{tab:freeBlockValues} 
\begin{center}
\begin{tabular}{|l| l|l| l|l|l|l|l|}
\hline
{\bf Time} & 
{\bf Location} &
{\it velError} & {\it penetration} & {\it posError} & {\it rhs} &
{\bf Velocity} & 
{\bf Impulse} \\  \hline
0.017 &  -0.003 & & & &  &-0.17 & 0 \\  \hline
0.533 &  -1.467 & & & & & -5.33 & 0 \\  \hline
0.550 &  -1.558 & & & & & -5.5 & 0 \\  \hline
0.567 &  -1.511 & 5.67 &-0.058 &2.8 &  21270 & 0.01 & 34000 \\  \hline
0.583 &  -1.502 & 0.14 &-0.011 & 0.54& 2570  & 0.55 & 420 \\  \hline
0.600 &  -1.496 & -0.38&-0.002 & 0.1  & -1000& 0.38 & 0 \\  \hline
0.617 &  -1.492 &-0.44 & 0.004 & 0     & -1600& 0.22 & 0 \\  \hline
0.717 &  -1.497 &0.004-0.08  &-0.0003-0.001 &0-0.01 & 10-400 & -0.01 & 400 \\  \hline
0.817 &  -1.499 & & & & & -0.08 & 700 \\  \hline
0.917 &  -1.500 & & & & & -0.001 & 1000 \\  \hline
\end {tabular}
\end{center}
\end {table}

\include{octave/uc-fig}

>>>>

Actual values for unconstrained case without continuous collision detection
are shown in Table \ref{tab:freeBlockValues} and 
location, velocity, posError and velError are depicted in Figure \ref{fig:uc}. 
Penetration is detected at time 0.567 s when
{\it velError} is 5.67 (5.5+0.167) and
{\it posError} is 2.8 (0.058*0.8/0.0167). Impulse is 34000 and contact force is thus about 2 MN (34000/0.0167).
After few steps location and position stabilize although internally calculation is needed for each time step
until body is deactivated.

\begin {table}[htb!]
\caption {Simulation values for unconstrained case without continuous collision detection. 
For internal contact values typical values are shown
as number of contacts and values at contact points are different.} 
\label{tab:freeBlockValues} 
\begin{center}
\begin{tabular}{|l| l|l| l|l|l|l|l|}
\hline
{\bf Time} & 
{\bf Location} &
{\it velError} & {\it penetration} & {\it posError} & {\it rhs} &
{\bf Velocity} & 
{\bf Impulse} \\  \hline
0.017 &  -0.003 & & & &  &-0.17 & 0 \\  \hline
0.533 &  -1.467 & & & & & -5.33 & 0 \\  \hline
0.550 &  -1.558 & & & & & -5.5 & 0 \\  \hline
0.567 &  -1.511 & 5.67 &-0.058 &2.8 &  21270 & 0.01 & 34000 \\  \hline
0.583 &  -1.502 & 0.14 &-0.011 & 0.54& 2570  & 0.55 & 420 \\  \hline
0.600 &  -1.496 & -0.38&-0.002 & 0.1  & -1000& 0.38 & 0 \\  \hline
0.617 &  -1.492 &-0.44 & 0.004 & 0     & -1600& 0.22 & 0 \\  \hline
0.717 &  -1.497 &0.004-0.08  &-0.0003-0.001 &0-0.01 & 10-400 & -0.01 & 400 \\  \hline
0.817 &  -1.499 & & & & & -0.08 & 700 \\  \hline
0.917 &  -1.500 & & & & & -0.001 & 1000 \\  \hline
\end {tabular}
\end{center}
\end {table}

\begin{figure}[htb!]
\centering
\input{figs/uc-fig.tikz}
\caption{Graph for selected values for unconstrained case simulation without continuous collision detection.}
\label{fig:uc}
\end{figure}
